\documentclass[12pt]{letter}
\usepackage[latin1]{inputenc}

\usepackage[left=1.00in, right=1.00in, top=1.00in, bottom=1.00in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\address{Andrew Rosen  \\ Georgia State University \\  rosen@cs.gsu.edu} 
\signature{Andrew Rosen} 
\date{}
\begin{document} 
\begin{letter}{Department of Electrical Engineering and Computer Science \\ Northwestern University} 
\opening{Dear Professors Larry Birnbaum, Uri Wilensky, and members of the Search Committee,} 
 
I am responding to your search for a tenure-track assistant professor of Computer Science and Learning Science posted on your departmental website.
I am currently a PhD candidate in the Department of Computer Science at Georgia State University, slated for graduation in May 2016.

I research fault-tolerant systems, with an emphasis on P2P systems, distributed computing, and Big Data applications.
One of my greatest frustrations when I stated doing research in distributed computing was that there were no trivial means to quickly deploy a distributed application.
A large portion of my research has focused on creating a platform called UrDHT.
This platform allows developers to easily create distributed applications and solve distributed computing.
I believe it will be of great use to researchers both inside and outside of Computer Science, as well as a valuable platform for teaching distributed computing to students.



I have a great passion for teaching and working with others.
I received the Outstanding Graduate Teaching award given by our Computer Science department in 2015.
I believe there is no reason that the basics of distributed computing cannot be integrated throughout all of a Computer Science curriculum, rather than being  reserved for a senior level or graduate class.

%The skills you asked for in the job posting.
I believe that my research's broad applications in Networking, Distributed Computing, and Big Data, plus my strong teaching and service backgrounds, make me an ideal candidate for your position.


\closing{Thank you for your consideration,} 
%\cc{Cclist} 
%\ps{adding a postscript} 
%\encl{list of enclosed material} 
\end{letter} 
\end{document}
