\documentclass[]{letter}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{cjhebrew}
%\usepackage{venturis2}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}
\date{October 27, 2017}
\begin{letter}{Many Places}
\address{Philadelphia,\\ L Train}

\opening{To my descendants,}

Sorry that has been a few weeks since I have written.
I haven't established this as habit yet.

Not much advice here, but I do have some news for you.  
Well, it's news to me; you might already know all about it.

I've been invited to teach Computer Science in Japan by my University's Japanese branch.
It is an amazing opportunity for many reasons.
The university will pay for me, Annie, and Lazer to all go, pay for our apartment there, so we can all experience it.
A free trip is nothing to easily say no to.
I've always wanted to go experience Japan and it's culture.
The most meaningful reason to me is that I've always wanted to go and teach internationally.

I'll probably be teaching introduction to programming using Java\footnote{Java was a popular programming language for the first programming course when I started my Bachelor's education in 2005(?), since it would run the same on all computers and you didn't have worry about esoteric errors like segfaults in C.  It currently (2017) has fallen slightly out of fashion for the first programming language in a number of schools, replaced by Python.} and a general introduction course for non-majors in Python.
These courses will be taught in English, so fortunately not being fluent in Japanese won't be an issue.

I did start teaching myself Japanese, as it will probably be foolish to be somewhere for 10 weeks and not be able to read the bus and train schedules.
More importantly however, language can reveal a lot about a culture and how people think, so learning it is a valuable experience.

My train is close to its stop; so this is it for now.
I'll try something more coherent in the next letter.
I hope you all get the opportunity to travel to far places and interesting destinations.
Be sure to send lots of pictures to me.

\signature{Professor Andrew Benjamin Rosen}

\closing{Your Ancestor }

%enclosure listing
%\encl{}


\begin{cjhebrew}
	.hnwK
\end{cjhebrew}
\end{letter}
\end{document}
